A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-21 paper/ms.tex
update ms

A third supporting line of evidence for the planetary interpretation
also exists, though we consider it less definitive than the stellar
density and TTV-local slope correlation.  We observed a transit of
\pn\ on the night of 2021 Aug 7 simultaneously with Keck/HIRES and
MuSCAT3.  We scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show the transit, and it appears to be achromatic
(Figure~\ref{fig:obliquity}, lower panels).  Fitting the MuSCAT3
photometry with a model that lets the transit depths vary across
bandpasses, we find {\it griz} depths consistent with the Kepler depth
at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  The MuSCAT3
observations also suggest a transit duration $17.4\pm3.6\,{\rm
minutes}$ shorter than the Kepler transits; further photometric
follow-up could help confirm whether such changes are indeed
happening.  For the RM analysis, the details are discussed in
Appendix~\ref{app:rm}.  While our RM data are marginally more
consistent with a prograde or polar orbit than a retrograde orbit,
given that the expected velocity anomaly ($\Delta v_{\rm RM}\approx
20\,{\rm m\,s}^{-1}$) is a factor of two smaller than the
spot-corrected exposure-to-exposure scatter, we are not in a position
to claim a spectroscopic detection of the RM effect, nor a precise
quantification of the stellar obliquity.

@@

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  Further
observations of spectroscopic transits could yield a more precise
stellar obliquity, and could confirm or refute the expected prograde
orbital geometry.  Similarly, transit spectroscopy aimed at detecting
outflows of hydrogen or helium could yield insight into the
evolutionary state of the atmosphere
\citep{spake_helium_2018,vissapragada_2020}.  Determining the precise
amount of high-energy irradiation incident on the planet would also
help in clarifying the expected outflow rate \citep[{\it
e.g.},][]{poppenhaeger_2021}.  Finally, a challenging but informative
quantity to measure would be the planet's mass.  This might be
possible through timing analyses of the Kepler data, or through a
high-cadence multi-color radial velocity campaign.  Measured at
sufficient precision, the mass could yield constraints on both the
planet's composition and its initial entropy
\citep{owen_constraining_2020}.

Separately, the Kepler data may yet contain further information.
Although our transit timing study did not yield the detection of any
planet-induced transit timing or transit duration variations,
Appendix~\ref{app:flare} highlights an odd flare timing coincidence
that may be suggestive of star-planet interactions.  We encourage its
exploration by investigators more versed in the topic than ourselves.

In the context of the transiting planet population, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages below 100\,Myr include K2-33, DS~Tuc~A, HIP~67522,
TOI~837, the two-planet AU~Mic system, and the four-planet V1298~Tau
system
\citep{Mann_K2_33b_2016,David_et_al_2017,newton_tess_2019,david_four_2019,bouma_cluster_2020,plavchan_planet_2020,martioli_aumicbc_2021}.
\pn\ is one of the smallest planets in this sample ($3.34\pm
0.18\,R_\oplus$), which could be linked to the selection effects
imposed by the spot-induced photometric variability at very young ages
\citep[{\it e.g.},][]{zhou_2021_tois}.  Assuming that these young
planets have masses between $\approx$5$\,M_\oplus$ and 10$\,M_\oplus$,
their large sizes and presumed low densities would be in accord with
the expectation that mini-Neptunes start their lives with large
primordial atmospheres that are shed over the first gigayear
\citep{Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018}.  Our
suggestion of an aligned orbit is consistent with a quiescent
disk-driven migration history, and differs from misalignments that
have been observed for some older
mini-Neptunes~\citep{sanchis-ojeda_starspots_2011,albrecht_obliquities_2012,dalal_2019_hd3167,rubenzahl_tess-keck_2021}.
Spectroscopic follow-up observations of the transit would however be
worthwhile to verify whether the TTV-slope correlation is yielding the
correct orbital geometry.

>>>>

A third supporting line of evidence for the planetary interpretation
also exists, though we consider it less definitive than the stellar
density and TTV-local slope correlation.  We observed a transit of
\pn\ on the night of 2021 Aug 7 simultaneously with Keck/HIRES and
MuSCAT3.  We scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show the transit, and it appears to be achromatic
(Figure~\ref{fig:obliquity}, lower panels).  Fitting the MuSCAT3
photometry with a model that lets the transit depths vary across
bandpasses, we find {\it griz} depths consistent with the Kepler depth
at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  The MuSCAT3
observations also suggest a transit duration $17.4\pm3.6\,{\rm
minutes}$ shorter than the Kepler transits; further photometric
follow-up could help confirm whether such changes are indeed
happening.  For the RM analysis, the details are discussed in
Appendix~\ref{app:rm}.  While our RM data are marginally more
consistent with a prograde or polar orbit than a retrograde orbit,
the expected velocity anomaly ($\Delta v_{\rm RM}\approx
20\,{\rm m\,s}^{-1}$) is a factor of two smaller than the
spot-corrected exposure-to-exposure scatter.  We are therefore not in
a position to claim a spectroscopic detection of the RM effect, nor a
precise quantification of the stellar obliquity.

@@

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  Further
observations of spectroscopic transits could yield a more precise
stellar obliquity, and could confirm or refute the expected prograde
orbital geometry.  Similarly, transit spectroscopy aimed at detecting
outflows of hydrogen or helium could yield insight into the
evolutionary state of the atmosphere
\citep{spake_helium_2018,vissapragada_2020}.  Determining the precise
amount of high-energy irradiation incident on the planet would also
help in clarifying the expected outflow rate \citep[{\it
e.g.},][]{poppenhaeger_2021}.  Finally, a challenging but informative
quantity to measure would be the planet's mass.  This might be
possible through long-term monitoring of the transit times and
durations, or through a high-cadence multi-color radial velocity
campaign.  Measured at sufficient precision, the mass could yield
constraints on both the planet's composition and its initial entropy
\citep{owen_constraining_2020}.

Separately, the Kepler data may yet contain further information.
Although our transit timing study did not yield the detection of any
planet-induced transit timing or duration variations,
Appendix~\ref{app:flare} highlights an odd flare timing coincidence
that may be suggestive of star-planet interactions.  We encourage its
exploration by investigators more versed in the topic than ourselves.

In the context of the transiting planet population, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages below 100\,Myr include K2-33, DS~Tuc, HIP~67522,
TOI~837, the two-planet AU~Mic system, and the four-planet V1298~Tau
system
\citep{Mann_K2_33b_2016,David_et_al_2017,newton_tess_2019,david_four_2019,bouma_cluster_2020,plavchan_planet_2020,martioli_aumicbc_2021}.
\pn\ is one of the smallest planets in this sample ($3.34\pm
0.18\,R_\oplus$), which could be linked to the selection effects
imposed by the spot-induced photometric variability at very young ages
\citep[{\it e.g.},][]{zhou_2021_tois}.  Assuming that these young
planets have masses between $\approx$5$\,M_\oplus$ and 10$\,M_\oplus$,
their large sizes and presumed low densities would be in accord with
the expectation that mini-Neptunes start their lives with large
primordial atmospheres that are shed over the first gigayear
\citep{Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018}.  Our
suggestion of an aligned orbit is consistent with a quiescent
disk-driven migration history, and differs from misalignments that
have been observed for some older
mini-Neptunes~\citep{sanchis-ojeda_starspots_2011,albrecht_obliquities_2012,dalal_2019_hd3167,rubenzahl_tess-keck_2021}.
Spectroscopic follow-up observations of the transit remain necessary
however to verify whether the TTV-slope correlation is yielding the
correct orbital geometry.
